---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# varde

<!-- badges: start -->
<!-- badges: end -->

The goal of varde is to provide functions for decomposing the variance in multilevel models, e.g., for g studies in generalizability theory or intraclass correlation analyses in interrater reliability.

## Installation

You can install the development version of varde from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jmgirard/varde")
```

## Example

In the `ppa` example dataset, 72 human "raters" judged the perceived physical attractiveness of 36 human "targets" in 6 different conditions (i.e., stimulus "types").

### Frequentist estimation using \{lme4\}

```{r res_1a, cache=TRUE}
library(varde)
fit_1a <- lme4::lmer(
  formula = Score ~ 1 + (1 | Target) + (1 | Rater),
  data = ppa
)
res_1a <- varde(fit_1a, ci = 0.95)
res_1a
plot(res_1a)
```

### Bayesian estimation using \{brms\}

```{r res_1b, message=FALSE, cache=TRUE}
fit_1b <- brms::brm(
  formula = Score ~ 1 + (1 | Target) + (1 | Rater),
  data = ppa,
  chains = 4,
  cores = 4,
  init = "random",
  warmup = 5000,
  iter = 10000,
  refresh = 0,
  silent = 2,
  seed = 2022
)
res_1b <- varde(fit_1b, ci = 0.95)
res_1b
plot(res_1b)
```

### More complicated example using \{lme4\}

```{r res_2, cache=TRUE}
fit_2 <- lme4::lmer(
  formula = Score ~ 1 + (1 | Target) + (1 | Rater) + (1 | Type) +
    (1 | Target:Rater) + (1 | Target:Type) + (1 | Rater:Type),
  data = ppa
)
res_2 <- varde(fit_2, ci = NULL)
res_2
plot(res_2)
```


