---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# varde

<!-- badges: start -->
<!-- badges: end -->

The goal of varde is to provide functions for decomposing the variance in multilevel models, e.g., for g studies in generalizability theory or intraclass correlation analyses in interrater reliability.

## Installation

You can install the development version of varde from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jmgirard/varde")
```

## Example

In the `ppa` example dataset, 72 human "raters" judged the perceived physical attractiveness of 36 human "targets" in 6 different conditions (i.e., stimulus "types").

### Simple Generalizability Study

```{r res_1, message=FALSE, cache=TRUE}
library(varde)

# Extract only type 1 observations (to simplify the example)
ppa_type1 <- ppa[ppa$Type == 1, ]

# Fit a mixed effects model with target and rater effects
fit_1 <- brms::brm(
  formula = Score ~ 1 + (1 | Target) + (1 | Rater),
  data = ppa_type1,
  chains = 4,
  cores = 4,
  init = "random",
  warmup = 5000,
  iter = 10000,
  seed = 2022
)

# Extract variance component estimates
res_1 <- varde(fit_1)
res_1

# Create density plot of variance posteriors
plot(res_1, type = "posterior")

# Create river plot of variance percentages
plot(res_1, type = "river", font_size = 4)
```

### Simple Two-Way ICC for Inter-Rater Reliability

```{r res_3, message=FALSE, cache=TRUE}
res_3 <- calc_icc(
  .data = ppa_type1, 
  subject = "Target",
  rater = "Rater",
  score = "Score"
)
res_3
```
